Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-31 paper/ijm.tex
Added descriptions of industry and occupation categories

\def\tenpc{$^{\ast}$}
\def\fivepc{$^{\ast\ast}$}
\def\onepc{$^{\ast\ast\ast}$}
\newcommand{\legend}{\normalsize{Significance levels:\hspace{1em} \tenpc : 10\% \hspace{1em} \fivepc : 5\% \hspace{1em} \onepc : 1\% \normalsize}}
\def\sep{0.5em}
\def\legendTwo{\multicolumn{3}{l}{\footnotesize{Significance levels
			:\hspace{1em} $\dag$ : 10\% \hspace{1em}
			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi} % needed for the tables produced by the esttab command in Stata, to avoid redundancy put here instead of in appendix.tex, where it is needed		
%SKB: Added for documenting the tables and figures
\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, marriage, number of children, inter-ethnic household}
\newcommand{\modelThree}{\modelTwo, industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}
\newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons 25-55 year old.}
\newcommand{\agerestrictions}{25-55 year olds only.}
% Modified section numbering: removed dot at the end as this jumps
% into the cross-references.
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}

@@

In this paper, we analyse the relationship between both
majority and minority language skills, and English for both
wage and unemployment. We analyse Estonia, a former Soviet republic
and now a rapidly growing and
transforming Easter European country. It is characterized by a stark linguistic division
where the Russian-speaking community forms almost 30\% of
the population. We use Estonian Labour Force Survey, one of the
higher-quality long-term datasets, well suitable for our
purpose. We provide long--term trends from the last years
of the planned economy in 1989 till the post-recession time in 2012.

@@

The Estonian economy, a part of the Soviet economy up to 1991, successfully
re-oriented to the Western markets and has been growing rapidly since
the mid-1990s. 
\Cref{fig:gdp_growth} shows that grew averaged at approximately 7\%
annually
before the financial crisis in 2008, afterwards the figure has been around 3\%.
As a by-product of the re-adjustment, English skills become extremely
valuable while the supply was still rather limited during the early
years of the transition.

@@

The effect of language fluency on unemployment is shown on
Figure~\ref{fig:long-run_unemployment}, and on wage on
Figure~\ref{fig:long-run_wage}.
The results reveal a few interesting facts. First, the effects are
relatively stable over time, indicating that neither the economic
environment nor the data quality have changed rapidly. Estonian language
fluency has been associated with less unemployment for both Russian men and
women since around the year 2000, in the 1990s it had little effect. Russian language fluency,
in contrast, had never had an impact on Estonians' unemployment probability.

>>>>

\def\tenpc{$^{\ast}$}
\def\fivepc{$^{\ast\ast}$}
\def\onepc{$^{\ast\ast\ast}$}
\newcommand{\legend}{\normalsize{Significance levels:\hspace{1em} \tenpc : 10\% \hspace{1em} \fivepc : 5\% \hspace{1em} \onepc : 1\% \normalsize}}
\def\sep{0.5em}
\def\legendTwo{\multicolumn{3}{l}{\footnotesize{Significance levels
			:\hspace{1em} $\dag$ : 10\% \hspace{1em}
			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi} % needed for the tables produced by the esttab command in Stata, to avoid redundancy put here instead of in appendix.tex, where it is needed		
%SKB: Added for documenting the tables and figures
\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, marriage, number of children, inter-ethnic household}
\newcommand{\modelThree}{\modelTwo, industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}
\newcommand{\industry}{Industry categories (according to NACE Rev.2): A Agriculture, Forestry and Fishing; B Mining and Quarrying; C Manufacturing; D Electricity, Gas, Steam and Air Conditioning Supply; E Water Supply;  Sewerage, Waste Management and Remediation Activities; F Construction; G Wholesale and Retail Trade;  Repair of Motor Vehicles and Motorcycles; H Transportation and Storage; I Accommodation and Food Service Activities; J Information and Communication; K Financial and Insurance Activities; L Real Estate Activities; M Professional, Scientific and Technical Activities; N Administrative and Support Service Activities; O Public Administration and Defence;  Compulsory Social Security; P Education; Q Human Health and Social Work Activities; R Arts, Entertainment and Recreation; S Other Service Activities; T Activities of Households as Employers;  Undifferentiate Goods and Services Producing Activities of Households for Own Use; U Activities of Extraterritorial Organisations and Bodies}
\newcommand{\occupation}{Occupation categories according to ISCO-08: 1 Managers; 2 Professional; 3 Technicians and associate professionals; 4 Clerical support workers; 5 Service and sales workers; 6 Skilled agricultural, forestry and fishery workers; 7 Craft and related trades workers; 8 Plant and machine operators, and assemblers; 9 Elementary occupations; 10 Armed forces occupations}
\newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons 25-55 year old.}
\newcommand{\agerestrictions}{25-55 year olds only.}
% Modified section numbering: removed dot at the end as this jumps
% into the cross-references.
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}

@@

In this paper, we analyse the relationship between both
majority and minority language skills, and English for both
wage and unemployment. We analyse Estonia, a former Soviet republic
and now a rapidly growing and
transforming Easter European country. It is characterized by a stark linguistic division
where the Russian-speaking community forms almost 30\% of
the population. We use the Estonian Labour Force Survey, one of the
higher-quality long-term datasets, well suitable for our
purpose. We provide long--term trends from the last years
of the planned economy in 1989 till the post-recession time in 2012.

@@

The Estonian economy, a part of the Soviet economy up to 1991, successfully
re-oriented to the Western markets and has been growing rapidly since
the mid-1990s. 
\Cref{fig:gdp_growth} shows that it grew averaged at approximately 7\%
annually
before the financial crisis in 2008, afterwards the figure has been around 3\%.
As a by-product of the re-adjustment, English skills become extremely
valuable while the supply was still rather limited during the early
years of the transition.

@@

The effect of language fluency on unemployment is shown in
Figure~\ref{fig:long-run_unemployment}, and on wage in
Figure~\ref{fig:long-run_wage}.
The results reveal a few interesting facts. First, the effects are
relatively stable over time, indicating that neither the economic
environment nor the data quality have changed rapidly. Estonian language
fluency has been associated with less unemployment for both Russian men and
women since around the year 2000, in the 1990s it had little effect. Russian language fluency,
in contrast, had never had an impact on Estonians' unemployment probability.
